Tropical Mathematics and the Lambda Calculus

### 2023-01-24 appVII.tex
Commit serale
commit

%
\begin{remark}\label{rem:functor}
Given $f:X\to Q$, $f$ is a functor precisely when for all $x,y\in X$ $f(x)\leq\inf_{x'\in X}f(x')+X(x',x)$. 
Indeed, if $f$ is a functor then $f(x)\leq f(x')+X(x',x)$, since $f(x)-f(x')=Q(f(x'),f(x))\leq X(x',x)$. 
Conversely, if $f(x)\leq f(x')+X(x',x)$ holds for all $x'$, then 
$Q(f(x),f(x'))=f(x')-f(x)\leq X(x',x)$. 
\end{remark}

\begin{remark}[Yoneda embedding]
%$\Lawv$ is a $\Lawv$-category with $Q(x,y)=|x-y|$. 
%For any $\Lawv$-category $X$ we can define a new $\Lawv$-category $\mathsf{Dist}(X,Q)$ (that we note simply as $[X,Q]$) whose objects are the distributors $x:\{\star\}\pfun X$, or equivalently, the functors from $X$ to $\Lawv$, i.e.~those $x\in \Lawv^{X}$ such that $|x_{a}-x_{b}|\leq X(a,b)$, or equivalently $x_{a}+X(a,b) \geq x_{b}$.

The \emph{Yoneda embedding} is the faithful functor $\B Y: X\to [X,Q]$ given by $\B Y(x)(y)=X(y,x)$. The functoriality and faithfulness of $\B Y$ follow from
\begin{align}
[X,Q](\B Y(x),\B Y(x'))= X(x,x') \tag{Yoneda}
\end{align}
which is proved as follows: for all $y\in X$ we have 
\begin{align*}
Q( \B Y(x)(y),\B Y(x')(y))&= \B Y(x')(y)-\B Y(x)(y) \\
&= X(y,x')-X(y,x) \leq X(x,x')
\end{align*}
where the last step follows from $X(y,x)+X(x,x')\geq X(y,x')$. 
From this we deduce that $[X,Q](\B Y(x),\B Y(x'))=\sup_{y\in X}Q( \B Y(x)(y),\B Y(x')(y))\leq X(x,x')$. 
For the converse direction, we have  
\begin{align*}
X(x,x') &  = X(x,x') - 0 \\ &=
X(x,x')- X(x,x)
\\& =\B Y(x')(x)-\B Y(x)(x)= Q(\B Y(x)(x),\B Y(x')(x))\\
&\leq [X,Q](\B Y(x), \B Y(x'))
\end{align*}
\end{remark}

\begin{remark}
The \emph{opposite Yoneda embedding} is the faithful functor
$\B Y^{\mathrm{op}}: X\to [X,Q]^{\mathrm{op}}$ given by $\B Y^{\mathrm{op}}(x)(y)=X(x,y)$. The functoriality and faithfulness of $\B Y^{\mathrm{op}}$ follow from
\begin{align}\label{eq:yonedaop}
[X,Q](\B Y^{\mathrm{op}}(x),\B Y^{\mathrm{op}}(x'))= X(x',x) \tag{Yoneda$^{\mathrm{op}}$}
\end{align}
which is proved similarly to the case of $\B Y$.
\end{remark}

@@

\begin{proposition}\label{prop:yonedasup}
Let $X$ be a skeletal $\Lawv$-category. Then $X$ is complete iff the Yoneda embedding has a left-adjoint.
\end{proposition}
\begin{proof}
 For all $ x\in [X,Q]$, let $\sup x$ be defined as a weighted colimit via
$$
X(\sup x, b)= \sup_{a\in X} X(a,b)-x_{a}
$$
that is, $\sup  x= \mathrm{colim}(  x, \mathrm{id}_{X})$, where $ x$ is seen as a distributor $x:\{\star\}\pfun X$.

Let us check that $\sup: [X,Q]\to X$ is a functor. First, let us check the  inequality
\begin{align}\label{eq:in1}
(X\multimapinv y)\cdot ( y\multimapinv x)\geq (X\multimapinv x)\end{align}
as follows:
\begin{align*}
\left((X\multimapinv  y)\cdot ( y\multimapinv x)\right)(a)&=
 \left (\sup_{b}X(b,a)- y_{b}\right)+\left(\sup_{b} y_{b}-x_{b}\right)\\
&\geq
\sup_{b}(X(b,a)- y_{b})+( y_{b}-x_{b})
\\
&=\sup_{b}(X(b,a)- y_{b}+ y_{b})-x_{b}
\\
&=\sup_{b} X(b,a)-x_{a}\\
&= (X\multimapinv x)(a)
\end{align*}
From \eqref{eq:in1} we deduce immediately the inequality below:
\begin{align}\label{eq:in2}
 y\multimapinv x \geq (X\multimapinv x)\multimapinv(X\multimapinv y)
\end{align}
and we can now compute:
\begin{align*}
[X,Q](x,  y)&= \sup_{a\in X} y_{a}-x_{a}\\
 &\stackrel{\tiny\eqref{eq:in2}}{\geq}
 \sup_{a\in X} \left( \sup_{b\in X}X(b,a)-x_{a}\right) -\left(  \sup_{b\in X}X(b,a)- y_{a}   \right )\\
 &= \sup_{a\in X}X(\sup x, a)-X(\sup  y, a)\\
 &= [X,Q](\B Y^{\mathrm{op}}(\sup y),\B Y^{\mathrm{op}}(\sup x))
 \tag{\ref{eq:yonedaop}}
 \\
&=X(\sup x, \sup  y)
\end{align*}

@@

Moreover, for all $x\in [X,Q]$, we have $\B Y(\sup x)\geq x$:  
\begin{align*}
\B Y(\sup x)(a) &= X(a,\sup x)\\
&= X(  \sup(\B Y(a)),\sup x) \\
& \geq [X,Q]( \B Y(a), x)\\
&\geq x_{a}-\B Y(a)(a) \\
&=
 x_{a}-X(a,a)  = x_{a}
\end{align*}
%where in the last step we use the fact that 
%$[X,Q](  \B Y(a),x)= \sup_{b}x_{b}-X(a,b) = x_{a}$.
%
%$ y\in \Lawv^{X}$, 
% $\| \B Y(\sup x)-  y\|_{\infty}=\| \B Y(\sup x)- x\|_{\infty}$. Indeed we have 
% \begin{align*}
% \| x_{a}-\B Y(\sup x)\|_{\infty}&= \sup_{a\in X}|
%x_{a}-\B Y(\sup x)(a)|\\ 
%&=
%\sup_{a\in X}|
%x_{a}-X(\sup x,a)|\\
% &=
%\sup_{a\in X}\inf_{a'\in X}| x_{a}+X(a',a) -x_{a'}|\\
%&= \sup_{a\in X}|x_{a}+ X(a,a)- x_{a}| = 0
% \end{align*}
%
%

@@

\begin{definition}[MacNeill Completion]
Let $X$ be a $\Lawv$-category. For all $f: \{\star\}\pfun X$ and $g:X\pfun \{\star\}$, let $f \coh g$ iff 
$f  = X\multimapinv g $ and 
$g = f\multimap X$. 
The \emph{MacNeill completion of $X$} is the $\Lawv$-category $\B M(X)$ made of those 
$f:\{\star\}\pfun X$ such that $f\coh g$ for some $g:X\pfun \{\star\}$, with
$\B M(X)(f,f')=[X,Q](f,f')$. 
\end{definition}

@@

%
%\begin{remark}[other notions of completeness]
%The categorical notion of completeness subsumes several other notions of completeness, in the sense of being (strictly) stronger:
%\begin{itemize}
%\item \emph{order-completeness} is the case when the pre-order $\preceq_{X}$ is complete.   
%Let $I\subseteq X$, so that $\mathrm{id}_{I}$ can be seen as a functor from the subcategory $I$ to $X$. Let $0_{I}: \{\star\}\pfun I$ be the distributor given by $(0_{I})_{i}=0$.
%Then $\mathrm{colim}(0_{I}, \mathrm{id}_{I})$ coincides with $\inf I$, via 
%$$
%X(\inf I, x) = \sup_{i\in I}X(i, x)
%$$
%Notice that in general an order-complete $\Lawv$-category needs not be tensored, and thus it needs not be complete.
%
%
%
%
% 
%
%\item \emph{Cauchy-completeness} is the case where $X$ contains the points $\sup x, \sup y$, for any 
% any two \emph{adjoint} presheaves $x, y\in [X,Q]$, i.e.~satisfying $0=\inf_{a}x_{a}+ y_{a}$ and $x_{a}+ x_{b}\geq X(a,b)$. 
% Notice that given a pair $(x,  y)$ we can define a Cauchy sequence by finding $a_{n}$ satisfying 
% $x_{a_{n}}+ y_{a_{n}}\leq \frac{1}{n}$. Indeed this implies $X(a_{n},a_{n+1})\leq x_{a_{n}}+ y_{a_{n+1}}\leq x_{a_{n}}+ y_{a_{n}}+x_{a_{n+1}}+ y_{a_{n+1}}=\frac{1}{n}+\frac{1}{n+1}$.
% Conversely, any (equivalence class of) Cauchy sequences $a_{n}$ yields an adjoint pair given by
% $x_{a}= \lim_{n}X(a_{n},a)$ and $ y_{a}=\lim_{n}X(a,a_{n})$. 
% 
%% 
%% \item \emph{Isbell-completeness} (or \emph{MacNeill completeness}) is the case where $X$ contains the points $\sup x, \sup  y$, for any two presheaves $x,  y\in [X,Q]$ satisfying 
%% $
%% x_{a}= \sup_{b\in X}X(b,a)- y_{b}
%% $.
%
%
%\end{itemize}
%
%\end{remark}

@@

\subsubsection{Tensors and $\Lawv$-Modules}

@@

\begin{lemma}
In any complete $\Lawv$-category, $x\otimes \epsilon \simeq \sup(  \B Y(x)+\epsilon  )$.
In the complete $\Lawv$-category $[X,Q]$, $x\otimes \epsilon= x+\epsilon$.
\end{lemma}
\begin{proof}
We have 
\begin{align*}
X(\sup(\B Y(x)+\epsilon), x')& =\sup_{y\in X}X(z,x')- (\B Y(x)(z)+\epsilon)\\
&= \sup_{y\in X}X(z,x')-(X(z,x)+\epsilon)\\
&= (\sup_{y\in X}X(z,x')-X(z,x))-\epsilon\\
&= X(x,x')-\epsilon
\end{align*}
which shows $x\otimes \epsilon=\sup(\B Y(x)+\epsilon)$. In $[X,Q]$ we have 
$[X,Q](x+\epsilon, x')=\sup_{a\in X}(x_{a}+\epsilon)-x'_{a}= (\sup_{a\in X}x_{a}-x'_{a})-\epsilon= [X,Q](x, x')-\epsilon$, which shows $x\otimes \epsilon \simeq x+\epsilon$, and since $[X,Q]$ is skeletal, $x\otimes \epsilon=x+\epsilon$.
\end{proof}

@@

\begin{example}
The $\Lawv$-category $[X,Q]$ is cotensored, with $x\multimapinv \epsilon:= x-\epsilon$. Indeed we have $[X,Q](x,  y\multimapinv \epsilon)=\sup_{a\in X}( y_{a}-\epsilon)-x_{a}=(\sup_{a\in X} y_{a}-x_{a})-\epsilon= [X,Q](x,  y)-\epsilon$.
\end{example}

@@

\begin{proposition}\label{prop:tencoten}
If a $\Lawv$-category $X$ is tensored, cotensored and order-complete, then it is complete.
\end{proposition}
\begin{proof}
For all $x\in [X,Q]$, let $\sup x:= \bigvee_{a\in X}a\otimes x_{a}$. 
Let us check that $X(\sup x, b)= \sup_{a\in X}X(a,b)-x_{a}$, using Lemma \ref{lemma:supinf}:
\begin{align*}
X(\sup x, b) &= \sup_{a\in X}X(a\otimes x_{a},b)\\
&=\sup_{a\in X}X(a,b)-x_{a}
\end{align*}
We can thus conclude using Proposition \ref{prop:yonedasup}.
\end{proof}

@@

%
%
%Let us first observe that:
%\begin{itemize}
%\item the hom-set $\Mod(M,N)$ of two $\Lawv$-modules is a $\Lawv$-module with order and action defined pointwise;
%
%\item for any $\Lawv$-module $M=(M,\preceq, \star)$, there is a $\Lawv$-module
%$M^{\mathrm{op}}=(M,\succeq, \multimapinv)$, with $\multimapinv$ defined as in the proof of Theorem \ref{thm:equivalence}.
%
%
%\end{itemize}
%
%
%
%Let $M,N$ be two $\Lawv$-modules. For all $A\in \Lawv^{M\times N}$, we define the function
%\begin{align*}
%H_{A} & : \Lawv^{M} \longrightarrow \Lawv^{N}%\\
%%K_{A} & : \Lawv^{N} \longrightarrow \Lawv^{M}
%\end{align*}
%via
%\begin{align*}
%H_{A}(x)(b)  &= \inf_{a\in M}x_{a}+A(a,b)\\
%%K_{A}(x)(b)  &= \sup_{a\in M}x_{a}-A(a,b)
%\end{align*}
%
%
%\begin{lemma}
%$H_{A}=H_{A'}$ iff $A=A'$. 
%\end{lemma}
%\begin{proof}
%We only need to prove one direction, so suppose $A\neq A'$ and let $a,b$ be such that $A(a,b)\neq A'(a,b)$.
%Let $x$ be defined by $x_{a}=1$ and $x_{a'}=\infty$ for all $a'\neq a$. Then $H_{A}(x)(b)=A(a,b)\neq A'(a,b)=H_{A'}(x)(b)$. 
%\end{proof}
%
%\begin{proposition}
%$\Lawv^{M\times N}$ and $\Mod(\Lawv^{M},\Lawv^{N})$ are isomorphic $\Lawv$-modules.
%\end{proposition}
%\begin{proof}
%The map $A\mapsto H_{A}$ is injective, as shown above. We need to check that it commutes with joins:
%\begin{align*}
%H_{\bigvee_{i}A_{i}}(x)(b) & = \inf_{a}x_{a}+\bigvee_{i}A_{i}(a,b)\\
%&=  \inf_{a}\bigvee_{i}x_{a}+A_{i}(a,b)\\
%&=  \bigvee_{i}\inf_{a}x_{a}+A_{i}(a,b)\\
%&=  \bigvee_{i}H_{A_{i}}(x)(b)\end{align*} 
%(recall that $\inf$s are actually joins in $\Lawv$!)
%
%We must prove that $H$ is surjective: for all $f\in \Mod(\Lawv^{M},\Lawv^{N})$, let 
%$k_{f}\in \Lawv^{M\times N}$ be given by $k_{f}(a,b)=f(e_{a})(b)$. 
%
%Then we have 
%\begin{align*}
%H_{k_{f}}(x)(b) & = \inf_{a}x_{a}+k_{f}(a,b) \\
%&= \inf_{a}x_{a}+ f(e_{a})(b)\\
%&= \left(\inf_{a}x_{a}+f(e_{a})\right)(b) \\
%&= \left(\inf_{a}f(x_{a}+e_{a})\right)(b) \\
%&= f(\inf_{a}x_{a}+e_{a})(b)\\
%&=
%f(x)(b)
%\end{align*}
%and conversely 
%\begin{align*}
%k_{H_{A}}(a,b)&= H_{A}(e_{a})(b)= \inf_{a'}(e_{a})_{a'}+A(a',b) =  A(a,b)
%\end{align*}
%\end{proof}
%
%
%More generally, we have the following result:
%\begin{proposition}
%Let $X,Y$ be two $\Lawv$-modules. For any morphism $f: X\to Y$ there is a matrix $k_{f}\in \Lawv^{X\times Y}$ such that 
%
%\end{proposition}
%\begin{proof}
%By composing $f$ with the isomorphisms $\B Y^{\mathrm{op}}:X\to \B M(X)$, with inverse $\sup(x)=\bigvee_{a\in x}a\otimes x_{a}$, we obtain 
%a morphism $\widehat f: \B M(X)\to \B M(Y)$  
%\begin{align*}
%\widehat f(x)(b)&:= \B Y^{\mathrm{op}}(f(\sup x))(b) \\
%&= Y( f(\bigvee_{a\in X}a\otimes x_{a}),b) \\
%&= Y( \bigvee_{a\in X}f(a)\otimes x_{a},b) \\
%&= \sup_{a\in X}Y(f(a),b)-x_{a}
%\end{align*}
%Observe that $\widehat f$ can be extended to a function $f^{*}$ from $\Lawv^{X}$ to $\Lawv^{Y}$.
%Now, $ f^{*}$ is generated by the matrix $k_{f}\in \Lawv^{X\times Y}$ given by $k_{ f}(a,b)=f(e_{a})(b)$, so that for all $x\in \Lawv^{X}$, 
%$f^{*}(x)(b)=\bigvee_{a\in X}k_{f}(a,b)+x_{a}$, and thus
%in particular, for all $x\in [X,Q]$, 
%$\widehat f(x)(b)=f^{*}(x)(b)$.
%\end{proof}

@@

\begin{proposition}
\begin{itemize}
\item[i.] $\Mod(Q,M)\simeq M$.
\item[ii.] $\Mod(M,N)\simeq \Mod(N^{\mathrm{op}},M^{\mathrm{op}})$.
\item[iii.] $\Mod(M, \Lawv^{\mathrm{op}})\simeq M^{\mathrm{op}}$.
\end{itemize}
(all isomorphisms of sup-lattices).
\end{proposition}
\begin{proof}
Define $\alpha:M\to \Mod(Q,M)$ by $\alpha(x)(\epsilon)=x\star\epsilon$ and 
$\beta:\Mod(Q,M)\to M$ by $\beta(f)=f(0)$. Then we have that 
$\alpha(\beta(f))(\epsilon)=\alpha(f(0))(\epsilon)=f(0)\star\epsilon=f(\epsilon)$, and 
$\beta(\alpha(x))=\beta(\lambda \epsilon.x\star\epsilon)=x\star0=x$.

@@

By i.~$\Mod(Q,M^{\mathrm{op}})\simeq M^{\mathrm{op}}$ and we conclude by ii.
\end{proof}

>>>>

%
\subsection{Proofs from Section \ref{section7}}

\begin{remark}\label{rem:functor}
Given $f:X\to \Lawv$, $f$ is a functor precisely when for all $x,y\in X$ $f(x)\leq\inf_{x'\in X}f(x')+X(x',x)$. 
Indeed, if $f$ is a functor then $f(x)\leq f(x')+X(x',x)$, since $f(x)-f(x')=\Lawv(f(x'),f(x))\leq X(x',x)$. 
Conversely, if $f(x)\leq f(x')+X(x',x)$ holds for all $x'$, then 
$\Lawv(f(x),f(x'))=f(x')-f(x)\leq X(x',x)$. 
\end{remark}

\begin{remark}[Yoneda embedding]
%$\Lawv$ is a $\Lawv$-category with $\Lawv(x,y)=|x-y|$. 
%For any $\Lawv$-category $X$ we can define a new $\Lawv$-category $\mathsf{Dist}(X,Q)$ (that we note simply as $[X,\Lawv]$) whose objects are the distributors $x:\{\star\}\pfun X$, or equivalently, the functors from $X$ to $\Lawv$, i.e.~those $x\in \Lawv^{X}$ such that $|x_{a}-x_{b}|\leq X(a,b)$, or equivalently $x_{a}+X(a,b) \geq x_{b}$.

The \emph{Yoneda embedding} is the faithful functor $\B Y: X\to [X,\Lawv]$ given by $\B Y(x)(y)=X(y,x)$. The functoriality and faithfulness of $\B Y$ follow from
\begin{align}
[X,\Lawv](\B Y(x),\B Y(x'))= X(x,x') \tag{Yoneda}
\end{align}
which is proved as follows: for all $y\in X$ we have 
\begin{align*}
\Lawv( \B Y(x)(y),\B Y(x')(y))&= \B Y(x')(y)-\B Y(x)(y) \\
&= X(y,x')-X(y,x) \leq X(x,x')
\end{align*}
where the last step follows from $X(y,x)+X(x,x')\geq X(y,x')$. 
From this we deduce that $[X,\Lawv](\B Y(x),\B Y(x'))=\sup_{y\in X}\Lawv( \B Y(x)(y),\B Y(x')(y))\leq X(x,x')$. 
For the converse direction, we have  
\begin{align*}
X(x,x') &  = X(x,x') - 0 \\ &=
X(x,x')- X(x,x)
\\& =\B Y(x')(x)-\B Y(x)(x)= \Lawv(\B Y(x)(x),\B Y(x')(x))\\
&\leq [X,\Lawv](\B Y(x), \B Y(x'))
\end{align*}
\end{remark}

\begin{remark}
The \emph{opposite Yoneda embedding} is the faithful functor
$\B Y^{\mathrm{op}}: X\to [X,\Lawv]^{\mathrm{op}}$ given by $\B Y^{\mathrm{op}}(x)(y)=X(x,y)$. The functoriality and faithfulness of $\B Y^{\mathrm{op}}$ follow from
\begin{align}\label{eq:yonedaop}
[X,\Lawv](\B Y^{\mathrm{op}}(x),\B Y^{\mathrm{op}}(x'))= X(x',x) \tag{Yoneda$^{\mathrm{op}}$}
\end{align}
which is proved similarly to the case of $\B Y$.
\end{remark}

@@

\begin{proposition}\label{prop:yonedasup}
Let $X$ be a skeletal $\Lawv$-category. Then $X$ is complete iff the Yoneda embedding has a left-adjoint.
\end{proposition}
\begin{proof}
 For all $ x\in [X,\Lawv]$, let $\sup x$ be defined as a weighted colimit via
$$
X(\sup x, b)= \sup_{a\in X} X(a,b)-x_{a}
$$
that is, $\sup  x= \mathrm{colim}(  x, \mathrm{id}_{X})$, where $ x$ is seen as a distributor $x:\{\star\}\pfun X$.

Let us check that $\sup: [X,\Lawv]\to X$ is a functor. First, let us check the  inequality
\begin{align}\label{eq:in1}
(X\multimapinv y)\cdot ( y\multimapinv x)\geq (X\multimapinv x)\end{align}
as follows:
\begin{align*}
\left((X\multimapinv  y)\cdot ( y\multimapinv x)\right)(a)&=
 \left (\sup_{b}X(b,a)- y_{b}\right)+\left(\sup_{b} y_{b}-x_{b}\right)\\
&\geq
\sup_{b}(X(b,a)- y_{b})+( y_{b}-x_{b})
\\
&=\sup_{b}(X(b,a)- y_{b}+ y_{b})-x_{b}
\\
&=\sup_{b} X(b,a)-x_{a}\\
&= (X\multimapinv x)(a)
\end{align*}
From \eqref{eq:in1} we deduce immediately the inequality below:
\begin{align}\label{eq:in2}
 y\multimapinv x \geq (X\multimapinv x)\multimapinv(X\multimapinv y)
\end{align}
and we can now compute:
\begin{align*}
[X,\Lawv](x,  y)&= \sup_{a\in X} y_{a}-x_{a}\\
 &\stackrel{\tiny\eqref{eq:in2}}{\geq}
 \sup_{a\in X} \left( \sup_{b\in X}X(b,a)-x_{a}\right) -\left(  \sup_{b\in X}X(b,a)- y_{a}   \right )\\
 &= \sup_{a\in X}X(\sup x, a)-X(\sup  y, a)\\
 &= [X,\Lawv](\B Y^{\mathrm{op}}(\sup y),\B Y^{\mathrm{op}}(\sup x))
 \tag{\ref{eq:yonedaop}}
 \\
&=X(\sup x, \sup  y)
\end{align*}

@@

Moreover, for all $x\in [X,\Lawv]$, we have $\B Y(\sup x)\geq x$:  
\begin{align*}
\B Y(\sup x)(a) &= X(a,\sup x)\\
&= X(  \sup(\B Y(a)),\sup x) \\
& \geq [X,\Lawv]( \B Y(a), x)\\
&\geq x_{a}-\B Y(a)(a) \\
&=
 x_{a}-X(a,a)  = x_{a}
\end{align*}
%where in the last step we use the fact that 
%$[X,\Lawv](  \B Y(a),x)= \sup_{b}x_{b}-X(a,b) = x_{a}$.
%
%$ y\in \Lawv^{X}$, 
% $\| \B Y(\sup x)-  y\|_{\infty}=\| \B Y(\sup x)- x\|_{\infty}$. Indeed we have 
% \begin{align*}
% \| x_{a}-\B Y(\sup x)\|_{\infty}&= \sup_{a\in X}|
%x_{a}-\B Y(\sup x)(a)|\\ 
%&=
%\sup_{a\in X}|
%x_{a}-X(\sup x,a)|\\
% &=
%\sup_{a\in X}\inf_{a'\in X}| x_{a}+X(a',a) -x_{a'}|\\
%&= \sup_{a\in X}|x_{a}+ X(a,a)- x_{a}| = 0
% \end{align*}
%
%

@@

\begin{definition}[MacNeill Completion]
Let $X$ be a $\Lawv$-category. For all $f: \{\star\}\pfun X$ and $g:X\pfun \{\star\}$, let $f \coh g$ iff 
$f  = X\multimapinv g $ and 
$g = f\multimap X$. 
The \emph{MacNeill completion of $X$} is the $\Lawv$-category $\B M(X)$ made of those 
$f:\{\star\}\pfun X$ such that $f\coh g$ for some $g:X\pfun \{\star\}$, with
$\B M(X)(f,f')=[X,\Lawv](f,f')$. 
\end{definition}

@@

%
%\begin{remark}[other notions of completeness]
%The categorical notion of completeness subsumes several other notions of completeness, in the sense of being (strictly) stronger:
%\begin{itemize}
%\item \emph{order-completeness} is the case when the pre-order $\preceq_{X}$ is complete.   
%Let $I\subseteq X$, so that $\mathrm{id}_{I}$ can be seen as a functor from the subcategory $I$ to $X$. Let $0_{I}: \{\star\}\pfun I$ be the distributor given by $(0_{I})_{i}=0$.
%Then $\mathrm{colim}(0_{I}, \mathrm{id}_{I})$ coincides with $\inf I$, via 
%$$
%X(\inf I, x) = \sup_{i\in I}X(i, x)
%$$
%Notice that in general an order-complete $\Lawv$-category needs not be tensored, and thus it needs not be complete.
%
%
%
%
% 
%
%\item \emph{Cauchy-completeness} is the case where $X$ contains the points $\sup x, \sup y$, for any 
% any two \emph{adjoint} presheaves $x, y\in [X,\Lawv]$, i.e.~satisfying $0=\inf_{a}x_{a}+ y_{a}$ and $x_{a}+ x_{b}\geq X(a,b)$. 
% Notice that given a pair $(x,  y)$ we can define a Cauchy sequence by finding $a_{n}$ satisfying 
% $x_{a_{n}}+ y_{a_{n}}\leq \frac{1}{n}$. Indeed this implies $X(a_{n},a_{n+1})\leq x_{a_{n}}+ y_{a_{n+1}}\leq x_{a_{n}}+ y_{a_{n}}+x_{a_{n+1}}+ y_{a_{n+1}}=\frac{1}{n}+\frac{1}{n+1}$.
% Conversely, any (equivalence class of) Cauchy sequences $a_{n}$ yields an adjoint pair given by
% $x_{a}= \lim_{n}X(a_{n},a)$ and $ y_{a}=\lim_{n}X(a,a_{n})$. 
% 
%% 
%% \item \emph{Isbell-completeness} (or \emph{MacNeill completeness}) is the case where $X$ contains the points $\sup x, \sup  y$, for any two presheaves $x,  y\in [X,\Lawv]$ satisfying 
%% $
%% x_{a}= \sup_{b\in X}X(b,a)- y_{b}
%% $.
%
%
%\end{itemize}
%
%\end{remark}

@@

\subsection{Tensors and $\Lawv$-Modules}

@@

\begin{lemma}
In any complete $\Lawv$-category, $x\otimes \epsilon \simeq \sup(  \B Y(x)+\epsilon  )$.
In the complete $\Lawv$-category $[X,\Lawv]$, $x\otimes \epsilon= x+\epsilon$.
\end{lemma}
\begin{proof}
We have 
\begin{align*}
X(\sup(\B Y(x)+\epsilon), x')& =\sup_{y\in X}X(z,x')- (\B Y(x)(z)+\epsilon)\\
&= \sup_{y\in X}X(z,x')-(X(z,x)+\epsilon)\\
&= (\sup_{y\in X}X(z,x')-X(z,x))-\epsilon\\
&= X(x,x')-\epsilon
\end{align*}
which shows $x\otimes \epsilon=\sup(\B Y(x)+\epsilon)$. In $[X,\Lawv]$ we have 
$[X,\Lawv](x+\epsilon, x')=\sup_{a\in X}(x_{a}+\epsilon)-x'_{a}= (\sup_{a\in X}x_{a}-x'_{a})-\epsilon= [X,\Lawv](x, x')-\epsilon$, which shows $x\otimes \epsilon \simeq x+\epsilon$, and since $[X,\Lawv]$ is skeletal, $x\otimes \epsilon=x+\epsilon$.
\end{proof}

@@

\begin{example}
The $\Lawv$-category $[X,\Lawv]$ is cotensored, with $x\multimapinv \epsilon:= x-\epsilon$. Indeed we have $[X,\Lawv](x,  y\multimapinv \epsilon)=\sup_{a\in X}( y_{a}-\epsilon)-x_{a}=(\sup_{a\in X} y_{a}-x_{a})-\epsilon= [X,\Lawv](x,  y)-\epsilon$.
\end{example}

@@

\begin{proposition}\label{prop:tencoten}
If a $\Lawv$-category $X$ is tensored, cotensored and order-complete, then it is complete.
\end{proposition}
\begin{proof}
For all $x\in [X,\Lawv]$, let $\sup x:= \bigvee_{a\in X}a\otimes x_{a}$. 
Let us check that $X(\sup x, b)= \sup_{a\in X}X(a,b)-x_{a}$, using Lemma \ref{lemma:supinf}:
\begin{align*}
X(\sup x, b) &= \sup_{a\in X}X(a\otimes x_{a},b)\\
&=\sup_{a\in X}X(a,b)-x_{a}
\end{align*}
We can thus conclude using Proposition \ref{prop:yonedasup}.
\end{proof}

@@

%
%
%Let us first observe that:
%\begin{itemize}
%\item the hom-set $\Mod(M,N)$ of two $\Lawv$-modules is a $\Lawv$-module with order and action defined pointwise;
%
%\item for any $\Lawv$-module $M=(M,\preceq, \star)$, there is a $\Lawv$-module
%$M^{\mathrm{op}}=(M,\succeq, \multimapinv)$, with $\multimapinv$ defined as in the proof of Theorem \ref{thm:equivalence}.
%
%
%\end{itemize}
%
%
%
%Let $M,N$ be two $\Lawv$-modules. For all $A\in \Lawv^{M\times N}$, we define the function
%\begin{align*}
%H_{A} & : \Lawv^{M} \longrightarrow \Lawv^{N}%\\
%%K_{A} & : \Lawv^{N} \longrightarrow \Lawv^{M}
%\end{align*}
%via
%\begin{align*}
%H_{A}(x)(b)  &= \inf_{a\in M}x_{a}+A(a,b)\\
%%K_{A}(x)(b)  &= \sup_{a\in M}x_{a}-A(a,b)
%\end{align*}
%
%
%\begin{lemma}
%$H_{A}=H_{A'}$ iff $A=A'$. 
%\end{lemma}
%\begin{proof}
%We only need to prove one direction, so suppose $A\neq A'$ and let $a,b$ be such that $A(a,b)\neq A'(a,b)$.
%Let $x$ be defined by $x_{a}=1$ and $x_{a'}=\infty$ for all $a'\neq a$. Then $H_{A}(x)(b)=A(a,b)\neq A'(a,b)=H_{A'}(x)(b)$. 
%\end{proof}
%
%\begin{proposition}
%$\Lawv^{M\times N}$ and $\Mod(\Lawv^{M},\Lawv^{N})$ are isomorphic $\Lawv$-modules.
%\end{proposition}
%\begin{proof}
%The map $A\mapsto H_{A}$ is injective, as shown above. We need to check that it commutes with joins:
%\begin{align*}
%H_{\bigvee_{i}A_{i}}(x)(b) & = \inf_{a}x_{a}+\bigvee_{i}A_{i}(a,b)\\
%&=  \inf_{a}\bigvee_{i}x_{a}+A_{i}(a,b)\\
%&=  \bigvee_{i}\inf_{a}x_{a}+A_{i}(a,b)\\
%&=  \bigvee_{i}H_{A_{i}}(x)(b)\end{align*} 
%(recall that $\inf$s are actually joins in $\Lawv$!)
%
%We must prove that $H$ is surjective: for all $f\in \Mod(\Lawv^{M},\Lawv^{N})$, let 
%$k_{f}\in \Lawv^{M\times N}$ be given by $k_{f}(a,b)=f(e_{a})(b)$. 
%
%Then we have 
%\begin{align*}
%H_{k_{f}}(x)(b) & = \inf_{a}x_{a}+k_{f}(a,b) \\
%&= \inf_{a}x_{a}+ f(e_{a})(b)\\
%&= \left(\inf_{a}x_{a}+f(e_{a})\right)(b) \\
%&= \left(\inf_{a}f(x_{a}+e_{a})\right)(b) \\
%&= f(\inf_{a}x_{a}+e_{a})(b)\\
%&=
%f(x)(b)
%\end{align*}
%and conversely 
%\begin{align*}
%k_{H_{A}}(a,b)&= H_{A}(e_{a})(b)= \inf_{a'}(e_{a})_{a'}+A(a',b) =  A(a,b)
%\end{align*}
%\end{proof}
%
%
%More generally, we have the following result:
%\begin{proposition}
%Let $X,Y$ be two $\Lawv$-modules. For any morphism $f: X\to Y$ there is a matrix $k_{f}\in \Lawv^{X\times Y}$ such that 
%
%\end{proposition}
%\begin{proof}
%By composing $f$ with the isomorphisms $\B Y^{\mathrm{op}}:X\to \B M(X)$, with inverse $\sup(x)=\bigvee_{a\in x}a\otimes x_{a}$, we obtain 
%a morphism $\widehat f: \B M(X)\to \B M(Y)$  
%\begin{align*}
%\widehat f(x)(b)&:= \B Y^{\mathrm{op}}(f(\sup x))(b) \\
%&= Y( f(\bigvee_{a\in X}a\otimes x_{a}),b) \\
%&= Y( \bigvee_{a\in X}f(a)\otimes x_{a},b) \\
%&= \sup_{a\in X}Y(f(a),b)-x_{a}
%\end{align*}
%Observe that $\widehat f$ can be extended to a function $f^{*}$ from $\Lawv^{X}$ to $\Lawv^{Y}$.
%Now, $ f^{*}$ is generated by the matrix $k_{f}\in \Lawv^{X\times Y}$ given by $k_{ f}(a,b)=f(e_{a})(b)$, so that for all $x\in \Lawv^{X}$, 
%$f^{*}(x)(b)=\bigvee_{a\in X}k_{f}(a,b)+x_{a}$, and thus
%in particular, for all $x\in [X,\Lawv]$, 
%$\widehat f(x)(b)=f^{*}(x)(b)$.
%\end{proof}

@@

\begin{proposition}
\begin{itemize}
\item[i.] $\Mod(\Lawv,M)\simeq M$.
\item[ii.] $\Mod(M,N)\simeq \Mod(N^{\mathrm{op}},M^{\mathrm{op}})$.
\item[iii.] $\Mod(M, \Lawv^{\mathrm{op}})\simeq M^{\mathrm{op}}$.
\end{itemize}
(all isomorphisms of sup-lattices).
\end{proposition}
\begin{proof}
Define $\alpha:M\to \Mod(\Lawv,M)$ by $\alpha(x)(\epsilon)=x\star\epsilon$ and 
$\beta:\Mod(\Lawv,M)\to M$ by $\beta(f)=f(0)$. Then we have that 
$\alpha(\beta(f))(\epsilon)=\alpha(f(0))(\epsilon)=f(0)\star\epsilon=f(\epsilon)$, and 
$\beta(\alpha(x))=\beta(\lambda \epsilon.x\star\epsilon)=x\star0=x$.

@@

By i.~$\Mod(\Lawv,M^{\mathrm{op}})\simeq M^{\mathrm{op}}$ and we conclude by ii.
\end{proof}
